Manuscript

### 2014-10-14 inst/simulation/manuscript.Rmd
...

p1 <- plotPopulationCorrelations(p1)
saveFigure(p1, "manuscript-figure-4a.png", width=4, height=4)
p2 <- plotPopulationCorrelations(p2)
saveFigure(p2, "manuscript-figure-4b.png", width=4, height=4)
p3 <- plotPopulationCorrelations(p3)
saveFigure(p3, "manuscript-figure-4c.png", width=4, height=4)
```

>>>>

p1 <- plotPopulationCorrelations(pc1)
saveFigure(p1, "manuscript-figure-4a.png", width=4, height=4)
p2 <- plotPopulationCorrelations(pc2)
saveFigure(p2, "manuscript-figure-4b.png", width=4, height=4)
p3 <- plotPopulationCorrelations(pc3)
saveFigure(p3, "manuscript-figure-4c.png", width=4, height=4)
```
